|

### 2021-12-15 curve-fitting-methods/curve-fitting-scratch.Rmd
minor update

\begin{enumerate}
  \item $p^{(s)} \leftarrow (T^\top T)^{-1} T^\top X$, 
where $T = \begin{bmatrix} \tilde{t}_1 & \cdots & \tilde{t}_n \end{bmatrix}^\top$ and 
$X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top$.
  \item $t_i^{(s)} \leftarrow \arg\min_t \|x_i - p^\top \tilde{t}_i\|^2$
\end{enumerate}
\end{theorem}

@@

>>>>

\begin{enumerate}
  \item $p \leftarrow (T^\top T)^{-1} T^\top X$, 
  where $T = \begin{bmatrix} \tilde{t}_1 & \cdots & \tilde{t}_n \end{bmatrix}^\top$ 
  and $X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top$.
  \item $t_i \leftarrow \arg\min_t \|x_i - p^\top \tilde{t}_i\|^2$,
  which can be solved by finding the roots of a polynomial of degree $2 R - 1$.
\end{enumerate}
\end{theorem}

@@

The objective function that this method aims to minimize is:

$$\sum_{k=1}^K \sum_{i \in C_k} \|x_i - g_k(t_i | p_k)\|^2$$

Where $g_k : [0, 1] \mapsto \mathbb{R}^d$ with parameters $p_k$ is the curve for community $k$.

It can be shown that each iteration decreases the objective unless we are at a stationary point.
